\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/eval.tex

%\aseem{I had a hard time parsing this. (1) Should we use $\cdot$ for
%  matrix multiplication as we did for DNNs? (2) Precedence of $\circ$
%  over scalar multiplication (or is it associative so doesn't matter?)
%(3) The argument to $f$ is a scalar (right?), and so is its output,
%so then is $\circ$ defined OR is it applying $f$ pointwise to a vector?}
%\nc{(1) I agree we should do that to be consistent with before. (2) I assumed $f()$ is computed to give a vector somehow and $I_j(x)W_j^TZx$ also gives a vector somehow and then we do $\circ$; I might be wrong. (3) Hmm.. I thought it was a vector, but I dont know how. (4) Can we specify somewhere the dimensions of these matrices?}
\[
{\sf argmax} \sum_{j = 0}^{N - 1} I_j(x)[ (W_j^T\matmul Z\matmul x) \circ (f(V_j^T\matmul Z\matmul x))] 
\]

Here, $I_j(x)$ is 1 if the $j^{th}$ node is present on the path traversed by $x$
and is zero otherwise. 
The operation $\circ$ is a pointwise multiplication of two vectors, $W_j$'s and $V_j$'s
are matrices of appropriate dimensions. The activation function $f$ is given by $f(y) = y$ if
$-1 < y < 1$ and $\mathrm{sign}(y)$ otherwise ($f$ on vectors and matrices is defined point-wise on every element of the vector/matrix).
%\bonsai can be
%seen as a variant of decision trees where the prediction is a function
%of the path traversed from root to the leaf and not just the leaf
%itself.

@@

 \caption{Partitioning results for CIFAR-10. \minion takes 544 seconds and communicates 9272 Mb to evaluate this DNN.}
 \label{tab:cifar} 
\end{table}

@@

 \caption{Partitioning results for matrix factorization. The time reported by~\cite{valeriaMatrix} for this computation is 10440 seconds.}
 \label{tab:factor} 
\end{table}
Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth stage, which is the heaviest. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
For this DNN, the specialized \minion protocol takes 544 seconds and
communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to arbitrary sized
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed.
\\\\
\noindent\textbf{Matrix factorization}
\tool, as a language, is not tied to secure prediction and can express more general computations.
To demonstrate the expressiveness of \tool, we use it to implement secure matrix factorization~\cite{valeriaMatrix}. Abstractly, given a sparse matrix $\mathcal{M}$ of dimensions
$n\times m$ and $M$ non-zero entries, the goal is to generate a matrix $U$ of dimension $n\times d$ and a matrix
$V$ of dimension $d\times m$ such that $\mathcal{M}\approx UV$. This operator is useful in recommender systems.
In particular, Nikolaenko et al.~\cite{valeriaMatrix} shows how to implement a movie recommender system which does not require users to reveal their data in the clear, i.e., the ratings the users have assigned to movies are kept secret. The implementation is a two party computation of an iterative algorithm for matrix factorization (Algorithm~1 in~\cite{valeriaMatrix}).
This algorithm is based on gradient descent and iteratively converges to a local minima.
We implement this algorithm in \tool.

>>>>

%\aseem{I had a hard time parsing this. (1) Should we use $\cdot$ for
%  matrix multiplication as we did for DNNs? (2) Precedence of $\circ$
%  over scalar multiplication (or is it associative so doesn't matter?)
%(3) The argument to $f$ is a scalar (right?), and so is its output,
%so then is $\circ$ defined OR is it applying $f$ pointwise to a vector?}
%\nc{(1) I agree we should do that to be consistent with before. (2) I assumed $f()$ is computed to give a vector somehow and $I_j(x)W_j^TZx$ also gives a vector somehow and then we do $\circ$; I might be wrong. (3) Hmm.. I thought it was a vector, but I dont know how. (4) Can we specify somewhere the dimensions of these matrices?}
\vspace{-10pt}
\[
{\sf argmax} \sum_{j = 0}^{N - 1} I_j(x)[ (W_j^T\matmul Z\matmul x) \circ (f(V_j^T\matmul Z\matmul x))] 
\]
Here, $I_j(x)$ is 1 if the $j^{th}$ node is present on the path traversed by $x$
and is zero otherwise. 
The operation $\circ$ is a pointwise multiplication of two vectors, $W_j$'s and $V_j$'s
are matrices of appropriate dimensions. The activation function $f$ is given by $f(y) = y$ if
$-1 < y < 1$ and $\mathrm{sign}(y)$ otherwise ($f$ on vectors and matrices is defined point-wise on every element of the vector/matrix).
%\bonsai can be
%seen as a variant of decision trees where the prediction is a function
%of the path traversed from root to the leaf and not just the leaf
%itself.

@@

 \caption{Partitioning results for CIFAR-10. \minion takes 544 seconds and communicates 9272 Mb.}
 \label{tab:cifar} 
\end{table}

@@

 \caption{Partitioning results for matrix factorization. The time reported by~\cite{valeriaMatrix} for this computation is 10440 seconds.}
 \label{tab:factor} 
\end{table}
Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth stage, which is the heaviest. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
For this DNN, the specialized \minion protocol takes 544 seconds and
communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to arbitrary sized
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed.
\\\\
\noindent\textbf{Matrix factorization}
\tool is not tied to secure prediction and can express more general computations.
To demonstrate this expressiveness, we  implement secure matrix factorization~\cite{valeriaMatrix}. Abstractly, given a sparse matrix $\mathcal{M}$ of dimensions
$n\times m$ and $M$ non-zero entries, the goal is to generate a matrix $U$ of dimension $n\times d$ and a matrix
$V$ of dimension $d\times m$ such that $\mathcal{M}\approx UV$. This operator is useful in recommender systems.
In particular, Nikolaenko et al.~\cite{valeriaMatrix} shows how to implement a movie recommender system which does not require users to reveal their data in the clear, i.e., the ratings the users have assigned to movies are kept secret. The implementation is a two party computation of an iterative algorithm for matrix factorization (Algorithm~1 in~\cite{valeriaMatrix}).
This algorithm is based on gradient descent and iteratively converges to a local minima.
We implement this algorithm in \tool.
